---
title: "ISSS608 Assignment Part 2"
description: |
  This post is a submission for ISSS608 Assignment 1, Vast Challenge 2 part 2
author:
  - name: Yeo Chia Guan Andy
    url: {}
date: 07-27-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# Install Required Packages

packages = c('DT','ggiraph','plotly','tidyverse', 'igraph','tidygraph','ggraph', 'sf',
             'visNetwork','lubridate','clock',
             'raster','tmap','clock','st','readr','mapview','ggpubr','greekLetters','widyr','tibble' )


for (p in packages){
  if(!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```


```{r}
# Import Data

car <- read_csv("data/car-assignments.csv")
gps <- read_csv("data/gps.csv")
credit_card <- read_csv("data/cc_data.csv")
loyalty <- read_csv("data/loyalty_data.csv")

```

```{r}
#Clean Credit Card and Loyalty Card Data

#Credit card
credit_card$last4ccnum <- as.character(credit_card$last4ccnum)

credit_card$timestamp <- date_time_parse(credit_card$timestamp,
                                 zone = "",
                                 format = "%m/%d/%Y %H:%M")

#Loyalty Card
loyalty$timestamp <- date_time_parse(loyalty$timestamp,
                                 zone = "",
                                 format = "%m/%d/%Y")
```

```{r}
#Left Join Loyalty Card transactions to credit card
credit_card$date <- as_date(credit_card$timestamp)

patronage <- credit_card %>%
  left_join(loyalty, by = c("date" = "timestamp", "location" = "location", "price" = "price"))

```

```{r}
#Splitting the date time into date, hours and minute
patronage$date <- as_date(patronage$timestamp)
patronage$hour <- hour(patronage$timestamp)
patronage$minute <- minute(patronage$timestamp)



```


```{r}
# Setting the Map as Background
bgmap <- raster("data/MC2-tourist_modified.tif")

#tmap_mode("plot")
#tm_shape(bgmap) + tm_raster(bgmap, legend.show = FALSE)

#tm_shape(bgmap) +
#tm_rgb(bgmap, r = 1, g = 2, b = 3,
#       alpha = NA,
#       saturation = 1,
#       interpolate = TRUE,
 #      max.value = 255)
```

```{r}
#Importing Abila Shape file into R
#Abila_st <- st_read(dsn = "data/Geospatial", layer = "Abila")

```


```{r}
#merging gps with car
vehicle <- gps %>%
  left_join(car, by = c("id" = "CarID"))
```

```{r}
vehicle$Timestamp <- date_time_parse(vehicle$Timestamp,
                                 zone = "",
                                 format = "%m/%d/%Y %H:%M:%S")

#Convert cars ID into Scalar Data-Type as each ID represents a vehicle
vehicle$id <- as_factor(vehicle$id)

```

```{r}
#Splitting Timestamp from vehicle into hours and minutes

vehicle$date <- as_date(vehicle$Timestamp)
vehicle$hour <- hour(vehicle$Timestamp)
vehicle$minute <- minute(vehicle$Timestamp)

```

```{r}
#Convert cars ID into Scalar Data-Type as each ID represents a vehicle
vehicle$id <- as_factor(vehicle$id)

```

```{r}
#Simple Frame for GPS data
vehicle_sf <- st_as_sf(vehicle,
                   coords = c("long", "lat"),
                   crs = 4326)
```


```{r}
#Creating a separate vehicle path by splitting the timestamp

vehicle_sf$date <- as_date(vehicle_sf$Timestamp)
vehicle_sf$hour <- hour(vehicle_sf$Timestamp)
vehicle_sf$minute <- minute(vehicle_sf$Timestamp)

```


```{r}
#Vehicle Path by employment type
jobtitle_path <- vehicle_sf %>%
  group_by(id,CurrentEmploymentTitle,CurrentEmploymentType,date,hour,minute) %>%
  summarise(m = mean(Timestamp),
            do_union=FALSE) %>%
  st_cast("LINESTRING")

```

```{r} 
#Remove single coordinates so that a line can be drawn for path data by date
r = mapview::npts(jobtitle_path, by_feature = TRUE)
jobtitle_path <- cbind(jobtitle_path, r)

```

### Vehicle Movement by Employment Type

When we look at the pathings by Employment Type, we see a different picture. As observed below, the Employment Type "Missing", which represents trucks (as identified with id > 100), showed a peculiar route taken. Vehicle *ID 107* could be seen travelling pass Pilau Park to Velestinou Boulevard.
Vehicle *ID 29* from Facilities could also be seen travelling to unique places during the period.

```{r}

#Plotting ppath by Employment Type
path_selected2 <- jobtitle_path %>%
  filter(r > "1")
tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(path_selected2) +
  tm_lines(by = "id") +
  tm_facets(by = "CurrentEmploymentType")

```


## 4.2 Finding Patterns from Patronage and Vehicle Data 

Next, we'll try and identify the possible owners of the credit card and loyalty card by filtering the location by date and time.
For the below charts, we filter the vehicle data to show the vehicle locations by hour, specifically on 6 Jan 2014.
The method applied was to identify the vehicle id which was present in on the map on a specific hour and cross-reference it to the paronage dataset to identify the credit card transaction made as well as the location.
The chart below is a sample used for the analysis. The charts were assessed by hours to determine the vehicle path by id by hour.



```{r}

#Plotting path on 6 Jan
path_selected_date <- jobtitle_path %>%
  filter(r > "1" & date == "2014-01-15" & hour == "9")
tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(path_selected_date) +
  tm_lines(by = "id") #+
 # tm_facets(by = "hour")

#patronage %>%
#  filter(date ="2014-01-13")

```
Vehicle Path on 15 Jan 14 at 9am


```{r}

#Plotting path on 6 Jan
path_selected_date <- jobtitle_path %>%
  filter(r > "1" & date == "2014-01-15" & hour == "10")
tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(path_selected_date) +
  tm_lines(by = "id") #+
 # tm_facets(by = "hour")

#patronage %>%
#  filter(date ="2014-01-13")

```
Vehicle Path on 15 Jan 14 at 10am

```{r}
patronage$location <- str_extract(patronage$location, regex("[:alpha:]*[:space:]*[:alpha:]*"))
DT::datatable(patronage)

```

### Isolated credit card transactions

The below observations using isolated cases could be made using the data from 6 Jan 14:



time (hr) |Vehicle ID | Location | last4ccnum
-----|-------|----------|------
9  | 101 | Kronos Pipe |  9220
10 |101 | Maximum Iron |  9220
10 | 107 | Nationwide Refinery |  9735
15  |104 | Abila Airport | 8642
20 | 19 | Shoppers | 7688



The steps above was repeated for all dates to obtain the below list of identified vehicle id, tagged to a credit card number. The rest of the data was not complete as during the process, several of the credit cards were found to be used at a shop where a different vehicle was driven instead. hence the technique was found to be lacking in terms of the accuracy.


Vehicle ID | last4ccnum
-------|-------
1 | 2681
10 | 1321
12 | 2418
13 |9735
14 | 5368
 19 |  7688
 21 | 8156
 24 | 9152 1877
 32 | 7688
 34 | 2681
35 | 9551
101 |   9220
104 |  8642
105 | 7792
107 |   9735
 

# 5.0 Future Works

As part of the future work, the network visualisation could be explored to match the credit card transactions to the vehicle id to identify the owners.


